---
title: "testing_cv"
author: "Argyris Stringaris"
date: "25/08/2022"
output: html_document
---
---
output:
  html_document: default
  word_document: default
  pdf_document: default
---

## Curriculum Vitae of Argyris Stringaris, MD, PhD, FRCPsych

**Professor and Chair of Child & Adolescent Psychiatry at University College London**


email: <argyris.stringaris@nih.gov>  
Address for Correspondence: 1-19 Torrington Pl, London WC1E 7HB, United Kingdom

Date: May 2022

### Overview

I am a clinician and neuroscientist. I was appointed Chair of Child and Adolescent Psychiatry at UCL in January 2022. Until then, I was Senior Investigator and Chief of the Section of Clinical and Computational Psychiatry at NIMH/NIH in the USA and before that a Senior Lecturer and a Wellcome Trust Fellow at the Institute of Psychiatry Psychology and Neuroscience, King's College London. I trained in Child and Adolescent Psychiatry at the Maudsley Hospital.

I have two main research aims.

In terms of basic research, my aim is to understand how affective phenomena (variably termed moods, emotions, feelings or affects) are generated and maintained.

In terms of clinical research, I study interventions that reduce the negative impact that affective phenomena, particularly depression, have on young people and families.

I am 47 years old, a husband and father of three daughters. I row
competitively on Concept2 and read hard-copy books.

Here is a [list of my
publications](https://pubmed.ncbi.nlm.nih.gov/?term=stringaris+a&sort=date)
and here is my [Google Scholar
page](https://scholar.google.com/citations?user=9B82424AAAAJ&hl=en&oi=ao).

### Current Positions

**Professor of Child and Adolescent Psychiatry**
Department of Psychiatry and Department of Clinical, Educational & Health Psychology
University College London

### Other positions

**Professor of Child and Adolescent Psychiatry**  
University of Athens, Greece

**Visiting Scientist and Head of the Clinical Neuroscience of Mood Disorders in Children and Adolescents**  
Central Institute of Mental Health (Zentralinstitut für Seelische Gesundheit), Mannheim, Germany


**Honorary Consultant Child & Adolescent Psychiatrist** 
Camden & Islington NHS Foundation Trust

### Degrees and Training

**Medical Training and Qualifications/Licenses to Practice**

  - May 2000 MBBS (MD) University of Göttingen, Germany. Top 3% of all
    German medical students in the 5th Year medical final examinations
    (II Staatsexamen) and top 20% of all students in 6th Year
    examination (III Staatsexamen)
    
  - Registration with the UK General Medical Council: 6043066   
  
  - Registration with the Maryland Board of Physicians by "Conceded Eminence": D48427
  
  - Entry into the UK Specialist Register for Child and Adolescent Psychiatry (CCT): 2011
  
  - Royal College of Psychiatrists Membership: 813569, Since 2018 a Fellow of the College.
  
  - Formerly Section 12 approved (lapsed since in the USA)
  
  - Hellenic Medical Council: Certified Specialist in Child and Adolescent Psychiatry


**Research Training**

  - PhD: King’s College London, University of London, UK, May 2011  
  - Research Fellow, Bipolar Spectrum Disorders, NIMH, USA, Jul 2008 –
    Jul 2009  
    
  - Dr med (MD Research), Department of Neurology, University of
    Göttingen, Germany, May 2000

**Training in Neurology and Psychiatry**

  - Aug 2006 – Apr 2011: Higher Specialist Training in Child and
    Adolescent Psychiatry, Maudsley Hospital and Great Ormond Street and
    Royal London Rotation  
  - Jul 2006: Membership, Royal College of Psychiatrists (MRCPsych,
    London, UK)  
  - Oct 2003 - Aug 2006: Senior House Officer, Maudsley Hospital,
    London, UK  
  - Oct 2002 - Oct 2003: Senior House Officer, Maudsley Hospital,
    London, UK and Institute of Psychiatry, London, UK  
  - Jun 2000 - Oct 2002: Neurology and Medicine, University of
    Göttingen, Germany

### Employment

  - August 2016 to 2021: Chief of Section of Clinical & Computational
    Psychiatry, NIMH, NIH
  - Jan 2012 - August 2016 Senior Lecturer 
    Head of Mood and Development Laboratory Consultant Child and
    Adolescent Psychiatrist (Attending Physician) Department of Child &
    Adolescent Psychiatry, Institute of Psychiatry, Psychology &
    Neuroscience, King’s College London & Maudsley Hospital London
  - Apr 2011 – August 2016: Consultant Psychiatrist at Maudsley Hospital
  - Jan 2007 - Jan 2012: Lecturer in Child and Adolescent Psychiatry at
    Institute of Psychiatry, King’s College London, London, UK with an
    interim period as Fellow at the National Institute of Mental Health,
    Bethesda, USA between July 2008 and July 2009.
  - Jan 2007 - Apr 2011: Specialist Registrar, Maudsley Hospital,
    London, UK
  - Aug 2006 - Dec 2006: Honorary Specialist Registrar in Child and
    Adolescent Psychiatry, Great Ormond Street and Royal London
    Rotation, London, UK
  - Apr 2006 – Aug 2006: Maudsley and King’s College Hospitals, General
    Liaison and Perinatal Psychiatry, London, UK
  - Oct 2002 - Aug 2006: Senior House Officer, South London and Maudsley
    NHS General Psychiatry Training Rotation, London, UK
  - Jun 2000 - Oct 2002: Senior House Officer (Assistenzarzt),
    Department of Neurology, University of Göttingen, Germany

### Scientific Leadership

**Presidency of International Organization**

  - President of the [International Society for
    Research in Child and Adolescent Psychopathology
    (ISRCAP)](https://isrcap.org/executive-committee.html)

**Journal Editorships**

  - Editor European Journal of Child and Adolescent Psychiatry (2021 -
    ongoing)
  - Consulting Editor Cognitive Affective and Behavioral Neuroscience
    (2021 - ongoing)
  - Editor (2012-2019) Journal of Child Psychology and Psychiatry
  - Editorial Board (2015 ongoing): Journal of the American Academy of
    Child & Adolescent Psychiatry

**Taskforce and Scientific Board Memberships** I have been invited to
participate as a member or scientific advisor in the following:
  - Member of the European College of Neuropharmacology (ECNP) Child and Adolescent Psychiatry Network. 
  - Member Scientific Advisory Group of Improving Adolescent mentaL health by reducing the Impact of       PoVErty
    (ALIVE), a Wellcome trust-funded international project. 
  - Scientific Board European Society of Child and Adolescent Psychiatry (ESCAP)
  - Member of European ADHD Guidelines Group (EAGG)
  - Member of the American Academy of Child and Adolescent Psychiatry Presidential
    Initiative Task Force on Emotion Regulation in Children : “Coming
    Together to Treat the Sickest Kids”- I was appointed chair of the
    Measurement Subcommittee
  - Member of the Program Committee for the American Academy of Child
    and Adolescent Psychiatry (AACAP) Annual meeting 2021
  - Scientific Advisory Board MQ The Mental Health Charity, UK
  - Member of the Task Force on Child and Youth Psychiatry of the World Federation of
    Societies of Biological Psychiatry (WFSBP)
  - Scientific Advisory Board Advisory Board for the Medical Research
    Council UK initiative in Adolescence, Mental Health and the
    Developing Mind

### Prizes
  - 2021 Open Neuro Hall of Fame, tied 2nd Place for contributing datasets
  - 2021 Kramer Pollnow Prize Award for scientific excellence in clinical research in   
    child,adolescent
    and adult psychiatry by the European Network of Hyperactivity Disorders (EUNETHYDIS)
  - 2020 Elaine Schlosser Lewis Award as the best research paper in ADHD
    research this year for the paper A Double-Blind Randomized
    Placebo-Controlled Trial of Citalopram Adjunctive to Stimulant
    Medication in Youth With Chronic Severe Irritability (first authors:
    Dr Kenneth Towbin, Dr Pablo Vidal-Ribas, see under Publications)
    that I am a last author on.
  - 2019 NIH Director’s Award “for exemplary performance while
    demonstrating significant leadership, skill and ability in serving
    as a mentor.”  
  - 2019 Gerald L Klerman Young Investigator (under 45 years) Prize, the
    highest honor that the Depression and Bipolar Support Alliance gives
    to members of the scientific community
  - 2019 Prize for Distinguished Editorial Contributions, Academy of
    Child and Adolescent Mental Health, J Child Psychol and Psychiatry
  - 2018 Elected a Fellow of the Royal College of Psychiatrists UK for
    Distinct and Significant Contributions to psychiatry.
  - 2018 Outstanding Mentor Award by the National Institutes of Mental
    Health
  - 2016 Special Commendation by the British Medical Association (BMA)
    for our book Disruptive Mood: Irritability in Children and
    Adolescents, published by Oxford University Press
  - 2014 Best Paper of the Year in Depression or Suicide published in
    JAACAP, awarded by the Klingenstein Foundation
  - 2010 Research Prize, European Psychiatric Association (EPA)  
  - 2004 Special Mention from the International Neuropsychiatry
    Association
  - 2004 European Science Foundation Young Scientist Travel Award

### Keynote Lectures, Invited Lectures, Symposia and Chairing of Symposia (examples)
  -Chair: ADHD. Life-time continuity, serious mental illness, and genetics World Psychiatric Association Thematic Conference, Athens, Greece
  - Guest Speaker and Panelist Pediatric Major Depressive Disorder Mini-Symposium,  Co-hosted by the Division of Pediatric and Maternal Health and the Division of Psychiatry Office of New Drugs | Center for Drug Evaluation & Research | U.S. Food and Drug Administration (FDA), (June 2022) Bethesda, MD, USA
  - Keynote Lecture (Lettura Magistrale) at the joint meeting of the Italian Societies of Neuropsychopharmacology       and Child & Adolescent Psychiatry (May 2022), Cagliari, Italy, Title: What is mood and how to modify it
  - Keynote Lecture (Hauptvortrag) at the German Society for Child and Adolescent Psychiatry (Deutsche Gesellschaft     für Kinder un      Jugendpsychiatrie, DGKJP, May 2022), Magdeburg Germany, Title: Warum gibt es Depression
  - Annual Distinguished Scientist Lecture at Pittsburgh University (April 2022) The Why and     How of Mood:           Theoretical and Computational Approaches for Clinicians and Researchers in      Depression. 
  - Opening Lecture at the European College of Neuropsychopharmacology (ENCP) at    
    Servolo,Venice (March 2022) Challenges and New Directions in Affective Nosology
  - Grand Rounds at Cornell University Department of Psychiatry (February 2022) What is mood?     A conceptual and      computational account of some basic questions about depression. 
  - Chair Symposium Irritability and Reactive Aggression: Implications
    for Diagnosis, Treatment, and Equity, American Academy of Child and
    Adolescent Psychiatry, October 2021
  - Maryland University Grand Rounds, May 2021
  - New York University, Langone, Grand Rounds May 2021
  - European Society for Child and Adolescent Psychiatry (ESCAP) Expert
    Day, June 2021
  - Royal College of Psychiatrists, Talk at Symposium S36 Dimensional
    and Categorical Psychopathology in Youth, Talk: Research in
    Depression, Great Expectations and Great Challenges, June 2021
  - Society for Biological Psychiatry, Talk at Symposium on
    Developmental Computational Psychiatry, Title: Adolescent Mood
    Dynamics, May 2021
  - Society for Biological Psychiatry, Talk at Symposium on Emerging
    Tools and Technologies, Title: What is Mood: In Search of Models of
    Mood Across Health and Disease, May 2021
  - Chair of the Symposium on Intergenerational Transmission of
    Psychopathology and Early Identification of Risk: New Insights From
    the Study of Child and Adolescent Offspring of Parents Living With
    Depression, Bipolar Disorder, and Schizophrenia, at the Academy of
    Child and Adolescent Psychiatry, San Francisco, USA, October 2020
  - Invited Speaker at University College London Institute of Mental
    Health First International Conference
  - Invited Speaker Canadian Academy of Child and Adolescent Psychiatry,
    Calgary, Canada, September 2020 (to be delivered online).
  - Invited Speaker, Dalhousie University, Halifax, Nova Scotia, Canada,
    September 2020 (to be delivered online). Panelist, Panel on
    Innovative Strategies for Transforming Treatment of Depression and
    Self-Harm, National Institutes of Health, September 2019
  - Invited Symposium Chair at the American Academy of Child and
    Adolescent Psychiatry (“Novel Approaches to Inform Treatment
    Decisions in Child Psychiatry: Steps Toward Personalized Medicine”)
    October 2019
  - Invited Lecture at Washington University in St Louis, Developmental
    Neuroimaging group, April 2019
  - Invited Lecture at the British Neuroscience Association (BNA) Annual
    Conference in Dublin, April 2019
  - Invited Lecture Oxford University’s Wolfson College at a workshop on
    experimental medicine of Treatment Resistant Depression, June 2019
  - Invited Keynote Lecture, Royal College of Psychiatrists, Child and
    Adolescent Psychiatry Annual Conference, Glasgow UK, September 2018
  - Invited Keynote Lecture, Scientific Society of Autism Spectrum
    Disorders (WGAS), Annual Conference, Augsburg, Germany, February
    2019
  - Grand Rounds (Weller Memorial Lecture), University of Pennsylvania,
    Philadelphia, June 2017
  - Invited Lecture, Laureate Institute, Tulsa, OH, August 2017
  - Grand Rounds at Georgetown University, Washington DC, July 2017
  - Grand Rounds at George Washington University, Washington DC, October
    2016
  - Invited Chairing of Session, Biannual Irritability Meeting,
    University of Vermont, Vermont, October 2017
  - Plenary Lecture, Stockholm University, Stockholm, Sweden, September
    2016
  - Invited Lecture, Oxford University, Oxford, UK, January 2014
  - Invited Lecture, University of Vermont, Biannual Irritability
    Meeting, Vermont, October 2015
  - Annual Meeting of the Royal College Lecture, Brighton, UK, September
    2015
  - Invited Lecture, Child Psychiatry Research Society, UK, July 2015,
  - Invited Lecture, Judge Baker Children’s Center, Harvard University,
    USA February 2111
  - Invited Lecture, Harvard Dept Psychology, February 2011

### Grants

  - Title: 4M: Microbes, Milk, Mental Health and Me; how do early life gut microbiota and feeding shape     long- term mental health in the C-GULL Cohort?  
    Position: Co-Investigator (5% of my time)   
    Funding Body: Wellcome Trust   
    Amount: £6,923,603.00  
    Dates: FY23 to FY 28  

  - Title: Respecting Affective Diversity in Adolescence (RADIANCE)  
    Position: Principal Investigator    
    Funding Body:Medical Research Council    
    Amount: Not Funded  
    

  - Title: Characterization and Treatment of Adolescent Depression
    (Identifying Number: ZIA MH002957-03)  
    Position: Principal Investigator  
    Funding Body: National Institutes of Mental Health  
    Amount: $ 12,7 Million 
    Dates: FY18 to FY 22

  - Title: Scoping review to systematically map the literature relating
    to the effects of SSRI treatment in young people aged 14-24 years
    old with depression and/or anxiety disorders.  
    Position: Co-PI  
    PI: Professor Catherine Harmer, Oxford University  
    Funding Body: Wellcome Trust, UK  
    Amount £ 45,000  
    Dates: FY 2020 to FY 2021

  - Title: Dynamics of mood fluctuations and brain connectivity in
    adolescent depression  
    Position Consultant, Grant number: 2019-175 PI: Dr Mattilde Vaghi
    Funding Body: Brain & Behavior Research Foundation Amount: $70,000  
    Dates: FY 2020 to FY 2021

  - Title: Ketamine for severe adolescent depression: intermediate-term
    safety and efficacy  
    Position: Consultant  
    PI: Dr Jennifer Dwyer, Yale University  
    Funding Body: Klingenstein Foundation  
    Amount: $60,000  
    Dates: 5/15/2019 - 5/14/2021

  - Title: Me\_Health\_e: testing the added value of electronic outcome
    measurement in Child & Adolescent Mental Health Services  
    Position: PI  
    Funding Body: Guys King’s St Thomas’s Charity  
    Amount: £87,500  
    Awarded: March 2016

  - Title: Validating the Case Register Interactive Search (CRIS) system
    for large naturalistic treatment trials in youth: A two-phase study
    using Attention Deficit Hyperactivity Disorder (ADHD) as a model.  
    Position: Co-PI with (Goodman, R., Pickles, A., Simonoff, E)  
    Funding Body: Guy’s & St Thomas’ Charity  
    Amount: £ 54,483.86 Dates: 2013 - 2014

  - Title: Ketamine’s Actions on Rumination Mechanisms as an
    Antidepressant (KARMA) Position: Co-PI with Drs Mehta and Curran  
    Funding Body: University College London and Johnson & Johnson
    Innovation Awards  
    Amount: £180,000  
    Awarded: September 2015

  - Title: Wellcome Trust Enhancement Award for Brain effects of
    lurasidone in a double blind, randomized placebo-controlled study.  
    Position CI  
    Funding Body: Wellcome Trust  
    Amount: £43,424  
    Awarded: March 2014

  - Title: A double-blind, randomized, placebo-controlled study of
    single-dose lurasidone effects on regional cerebral blood flow,
    emotion- and reward-processing.  
    Position CI  
    Funding Body: National Institute of Health Research (BRC)  
    Amount: £39, 000  
    Awarded: December 2013

  - Title: Validating the Case Register Interactive Search (CRIS) system
    for large naturalistic treatment trials in youth: A two-phase study
    using Attention Deficit Hyperactivity Disorder (ADHD).  
    Position: CI  
    Funding Body: Biomedical Research Centre  
    Amount: £54,483  
    Awarded: February 2013

  - Title: Arterial Spin Labelling to study mood regulation in youth.  
    Position: CI  
    Funding Body: Biomedical Research Centre  
    Amount: £15,000  
    Awarded: December 2012

  - Title: Behavioural and Emotional Dimensions in Children, Award ID:
    089/0001  
    Position: Co-PI (with Professor Marjorie Smith from the Institute of
    Education leading) Funding Body: Department of Health  
    Amount: £437,194.97  
    Awarded: 2011

  - Title: The developmental psychopathology of irritable mood and its
    links to depression: genetic and environmental risks,
    neuropsychological mechanisms, and hormonal influences, Project
    code: 093909  
    Position: CI Funding Body: Wellcome Trust, Intermediate Clinical
    Fellowship  
    Amount: £439,243  
    Awarded: April 2011

### Mentorship and Teaching  

**Mentorship Awards**  
I have recently received two prizes for my mentorship at NIH, namely the 
  - 2019 NIH Director’s Award “for exemplary performance and significant leadership, skill and ability in serving as a mentor.”
  - 2018 Outstanding Mentor Award by the National Institutes of Mental Health

**Fulbright Fellow**

  - Dr Neny Pervanidou, Associate Professor of Developmental Pediatrics
    spent six months in our Unit after being awarded this prestigious
    fellowship. This has laid the foundations for an ongoing
    collaboration.

**Post-doctoral fellows**

  - Dr Lorena Fernandez de la Cruz, currently Assistant Professor at
    Karolinska Institutet

  - Dr Narun Pornpattatanangkul, currently Faculty at Ottago University

  - Dr Georgia O’ Callaghan, currently Senior Principal Analyst at
    Gartner

  - Dr Hanna Keren, hired as faculty with Bar Ilan University at Israel

  - Dr Dipta Saha, currently post-doc at NIH

  - Dr Song Qi, currently post-doc at NIH

  - Dr Lucrezia Liuzzi, moved on to be Staff Scientist at NIH

**PhD Students**

  - Mr Jiazhou Chen, August 2020 - Current

  - Ms Marie Zelenina, August 2020 - Current

  - Dr Nina Mikita: PhD awarded “without corrections” June 2016

  - Dr Selina Wolke: PhD awarded “without corrections” May 2018

  - Dr Pablo Vidal-Ribas: PhD awarded “without corrections” March 2019
    Awarded one of the 2019 Outstanding PhD Thesis Prizes from King’s
    College London.

**MSc Students**

I have mentored between 2009-2015 nine MSc students for the course in
Child and Adolescent Psychiatry at King’s College London. Many of them
won distinctions, such as Dr Sumudu Ferdinando who came first in her
cohort for that year with top marks for her dissertation.

**Other post-graduate Students**

I have mentored between 2016 to Present more than 10 Intramural Research
Technical Assistants (IRTAs) in the intramural programme of the NIMH.
Each one of them has ended up pursuing their career of interest with
several of them joining prestigious courses in medicine in the US
(e.g. Ms Lisa Gorham, Washington University at St Louis), Clinical
Psychology or Psychology courses (e.g. Mr Chris Camp, Yale University).

### Taught Courses and other Supervision

  - Exam marker at UCL's Depression and Anxiety MSc module
  
  - Lecturer at UCL's Child and Adolescent Mental Health MSc
  
  - Dissertation Supervisor at UCL's Child and Adolescent Mental Health MSc
  
  - Academic Training Director for Trainees in Child Psychiatry. I had
    volunteered to be the Academic Director of the Maudsley Hospital’s
    Child Psychiatry Training Scheme. In this position I was responsible
    for the content and process of trainees’ academic learning. This
    included organizing speaker series, modifying training content,
    assessing competencies of trainees in relation to the expected
    curriculum and devising innovative ways to improve teaching. 2010 -
    2016

  - Member of the Institute of Psychiatry, Psychology and Neurosience
    (IoPPN) PhD Committee represeneting the Department of Child and
    Adolescent Psychiatry, 2012- 2016

  - Supervisor of SpRs/ST4s at the Maudsley Hospital Rotation Scheme,
    (2010-2016) at the Maudsley National and Specialist Mood Disorder
    Service

  - Taught regularly at the Maudsley Hospital’s Child Psychiatry
    Training Scheme on the topics of Depression and Bipolar Disorder
    (2010 - 2016)

  - Taught regularly at the (Social Genetic and Developmental Psychiatry
    MSc) at King’s College London, (2012-2016)

### Voluntary contributions to the Scientific Community

  - Member of the Senior Investigator and Tenure Track Investigator NIMH
    Search Committee for the recruitment of new PIs to NIH.

  - Organized 2018 Suicide Workshop at NIMH

  - Soon after my arrival at NIMH, I organized a Workshop about suicide
    recognition and prevention with four invited speakers from within
    the NIMH and elsewhere. It was attended physically by over 260
    registered participants and we received good feedback from attendees
    (many of whom were practitioners).

  - Organization of Faculty Retreats. I have been an active member of
    the Faculty Retreat Committee and has so far given talks at three
    out of the four faculty retreats that have happened since my arrival
    at NIMH.

  - Securing of competitive funds for Academic Clinical Fellow
    positions. I have secured competitive funding for these academic
    posts of junior doctors for my Department in the UK for three
    consecutive years, since I took over this responsibility as Academic
    Programme Director in 2013: 2014-2015, 2015-2016 and 2016-2017.

  - Representative of the Department at the Equality and Diversity
    Committee of my Institution. I was part of the original “Athena
    SWAN” team that assessed the situation in relation to women’s
    academic positions at our institution (King’s College London) and
    the need to improve it. I was part of the team that devised and
    analyzed results of an employee survey on this matter and
    communicated it to individuals. I also represented my Department at
    such meetings. Our team’s efforts were recognized by the Government
    and our Institution was awarded a Bronze Medal for championing the
    role of women in STEM.

  - Refereeing for Journals. I am acting as referee or ad hoc editor for
    a broad range of journals including: JAACAP, JCPP, JAMA Psychiatry,
    Am J Psychiatry, Biol Psychiatry, ECAP, eLife. I referee about 2-3
    papers per week.

  - Refereeing for Funding bodies. I am acting as referee for several
    funding organization including: Wellcome Trust, MRC(UK),
    MRC(Australia), Israeli Science Foundation.

  - Examiner for PhDs in other Universities, such as the following:
    Oxford University PhD in Psychology, Neuroimaging and Pharmacology;
    Cambridge University PhD in Psychology and Neuroimaging; Cardiff
    University, PhD in Psychology and Epidemiology; Lisbon University,
    PhD in Computational Psychiatry; Sheffield University, PhD in
    Developmental Psychology, Örebro University, Sweden.


### Response to the Coronavirus Pandemic (COVID-19)

My team and I have been at the forefront of the response to the
potential mental health consequences of the pandemic in the following
ways.

  - Development of Resources for the measurement and tracking of
    pandemic-related psychological problems: I am on of the three people
    who developed the CRISIS initiative (Coronavirus Health Impact
    Survey, <http://www.crisissurvey.org> ), the other two being Drs
    Merikangas (NIMH) and Dr Milham (Child Mind Institute). This is a
    tool for parents, children and adults to track phenomenal related to
    the pandemic. It has been translated into several languages
    including Mandarin Chinese, Greek, Japanese, Italian, French, German
    and Portuguese. It is used by more then 15 teams worldwide.

  - Help with translation of questionnaires in different languages: I
    have organized most translations of the CRISIS tool, including the
    back-translations and attempts at swift quality assurance. I have
    myself helped with the translations into German and Greek.

  - Participation in international grants and projects: I have helped
    more than 5 teams by consulting on their projects and grants
    internationally, including in the USA, Australia, New Zealand,
    Greece, and the UK. These will be listed in the grants section
    depending on the outcome of the proposals.

  - Collection of longitudinal data within our own team: Ours was the
    first protocol to be amended at NIMH in order to collect data
    related to COVID distress. We are collecting longitudinal data (we
    have already completed 3 waves of data collection) and are expected
    to collect several more which we will be using in conjunction with
    our longitudinal data.

### Other activities 
- Sports: I row competitively on Concept 2 and in 2021 I ranked worldwide for the 40-49 age range in the 97th percentile in 2000m (6:36.8), 97th percentile in 5000 m (17:49.3), and 91st percentile in the half marathon (1:21:40.1). In the 2023 season, I raced 5000 m 17:56.8. 

- Philosophy: I am working on the relevance of the work of Panajotis Kondylis, particularly his Macht und Entscheidung, to emotion theory, as well as issues related to the conceptual history of mood inspired from Reinhart Kosselleck's work on Begriffsgeschichte. Some of these results I presented at my keynote at the European Child and Adolescent Psychiatry Conference this year.


### Publications  

**Bibliographic Overview**  
h-index 54, n_citations = 12454 (Google Scholar July 2022)

**Monographs**

**Stringaris** A & Taylor E (2015). Disruptive Mood: Irritability in
Children and Adolescents. New York: Oxford University Press.

**Book Chapters**

1 Prabhakar J, Nielson DM, **Stringaris** (2022) Origins of Anhedonia in Childhood and Adolescence,In Pizzagali D (Ed) Current Topics in Behavioural Neuroscience. Springer 

2 O’Callaghan, G. & **Stringaris**, A (2019) Reward Processing in
Adolescent Depression. In C Harmer & T. Baune (Eds.) Cognitive
Dimensions of Major Depressive Disorder, Oxford University Press

 **Stringaris**, A., & Vidal-Ribas, P. (2018). Disruptive Mood
Dysregulation Disorder. In M. Ebert, J. Leckman & I. Petrakis (Eds.),
Current Diagnosis & Treatment Psychiatry (Third ed.): Lange Medical
Books/McGraw-Hill.

4 Zahredine N, **Stringaris** A (2018) Bipolar Illness in Children and
Adolescents, The Maudsley Prescribing Guidelines, Ed Taylor D, Barnes
TRE, Young AH. Wiley Blackwell

5 Vidal-Ribas, P., & **Stringaris**, A. (In press). Irritability in Mood
and Anxiety Disorders. In A. K. Roy, M. A. Brotman & E. Leibenluft
(Eds.), Irritability in Pediatric Psychopathology: Oxford University
Press.

6 Oxley C, **Stringaris** A (2018) Comorbidity of Depression and Anxiety
with ADHD. In Oxford Textbook of Attention Deficit Hyperactivity
Disorder. Ed. Banaschewski T, Coghill D, Zuddas A. Oxford University
Press

7 Mulraney M, **Stringaris** A, Taylor A (2018). Irritability,
disruptive mood and ADHD. In Oxford Textbook of Attention Deficit
Hyperactivity Disorder. Ed. Banaschewski T, Coghill D, Zuddas A. Oxford
University Press

8 Krieger FV and **Stringaris** A (2015). Temperament and Vulnerability
to Externalizing Behavior in The Oxford Handbook of Externalizing
Spectrum Disorders, Eds. Beauchaine TP and Hinshaw S. New York: Oxford
University Press.

9 **Stringaris** A (2015). Emotion regulation and emotional disorders:
conceptual issues for clinicians and neuroscientists in Rutter’s Child
and Adolescent Psychiatry, Sixth Edition, Eds. Thapar A, Pine DS,
Leckman JF, Scott S, Snowling MJ, Taylor EA. Oxford: Wiley-Blackwell.

10 **Stringaris** AK, Asherson P (2008). Molecular Genetics in Child
Psychiatry in Advances in Biological Child Psychiatry, Eds. Rohde LA,
Banaschewski, T. Basel: Karger Publishing.

11 Giora R, **Stringaris** AK (2008). Neural Substrates of Metaphors in
The Cambridge Encyclopedia of the Language Sciences (CELS), Ed. Hogan
PC. New York: Cambridge University Press.



**Book Editorship**

1 Thapar A, Pine D, **Stringaris** A, Ford T, Cresswell C, Cortese S,
Leckman J (in preparation) Rutter’s Textbook of Child Psychiatry and
Psychology, Oxford, UK: Wiley Blackwell

2 Broome MR, Harland R, Owen GS, **Stringaris** A (2012). The Maudsley
Reader in Phenomenological Psychiatry. Cambridge, UK: Cambridge
University Press.

**Publications as Preprints**

1 Jangraw DC, Keren H, Bedder RL, Rutledge RB, Perreira F, Thomas AG,
Pine DS, Zheng C, Nielson, DM , **Stringaris** A (2021) Passage-of-Time
Dysphoria: A Highly Replicable Decline in Mood During Rest and Simple
Tasks that is Moderated by Depression, Psyarxiv preprint


```{r}
library(tidyverse)
Chapters <- c("Prabhakar J, Nielson DM, Stringaris (2022) Origins of Anhedonia in Childhood and Adolescence,In Pizzagali D (Ed) Current Topics in Behavioural Neuroscience. Springer",
        
"O’Callaghan, G. & Stringaris, A (2019) Reward Processing in Adolescent Depression. In C Harmer & T. Baune (Eds.) Cognitive Dimensions of Major Depressive Disorder, Oxford University Press",
 
 "Stringaris, A., & Vidal-Ribas, P. (2018). Disruptive Mood Dysregulation Disorder. In M. Ebert, J. Leckman & I. Petrakis (Eds.), Current Diagnosis & Treatment Psychiatry (Third ed.): Lange Medical Books/McGraw-Hill.",

"Zahredine N, **Stringaris** A (2018) Bipolar Illness in Children and Adolescents, The Maudsley Prescribing Guidelines, Ed Taylor D, Barnes TRE, Young AH. Wiley Blackwell",

"Vidal-Ribas, P., & **Stringaris**, A. (In press). Irritability in Mood and Anxiety Disorders. In A. K. Roy, M. A. Brotman & E. Leibenluft (Eds.), Irritability in Pediatric Psychopathology: Oxford University Press.",

"Oxley C, **Stringaris** A (2018) Comorbidity of Depression and Anxiety with ADHD. In Oxford Textbook of Attention Deficit Hyperactivity Disorder. Ed. Banaschewski T, Coghill D, Zuddas A.Oxford University Press",

"Mulraney M, **Stringaris** A, Taylor A (2018). Irritability, disruptive mood and ADHD. In Oxford Textbook of Attention Deficit Hyperactivity Disorder. Ed. Banaschewski T, Coghill D, Zuddas A. Oxford University Press",

"Krieger FV and **Stringaris** A (2015). Temperament and Vulnerability to Externalizing Behavior in The Oxford Handbook of Externalizing Spectrum Disorders, Eds. Beauchaine TP and Hinshaw S. New York:Oxford University Press.",

"**Stringaris** A (2015). Emotion regulation and emotional disorders: conceptual issues for clinicians and neuroscientists in Rutter’s Child and Adolescent Psychiatry, Sixth Edition, Eds. Thapar A, Pine DS, Leckman JF, Scott S, Snowling MJ, Taylor EA. Oxford: Wiley-Blackwell.",

"**Stringaris** AK, Asherson P (2008). Molecular Genetics in Child Psychiatry in Advances in Biological Child Psychiatry, Eds. Rohde LA, Banaschewski, T. Basel: Karger Publishing.",

"Giora R, **Stringaris** AK (2008). Neural Substrates of Metaphors in The Cambridge Encyclopedia of the Language Sciences (CELS), Ed. Hogan PC. New York: Cambridge University Press."
)


data.frame(Chapters) %>% 
  knitr:: kable("simple")

```



**Journal Publications**  
```{r, echo=FALSE, message=FALSE}
library(stringr)
library(tidyverse)

test_pub_med <- read.csv("~/Downloads/csv-stringaris-set (3).csv")
test_pub_med$Authors <- str_replace_all(test_pub_med$Authors, "Stringaris", "**Stringaris**") 


test_pub_med<- test_pub_med %>% 
  filter(str_detect(Authors, "Stringaris")) %>% 
  dplyr:: select("Authors", "Title", "Journal.Book", "PMID", "Publication.Year") 


test_pub_med$number_of_row <- seq.int(nrow(test_pub_med))

PubMed <- 0# matrix(NA, nrow = nrow(test_pub_med), ncol = 1)
for (i in 1: nrow(test_pub_med)){
PubMed[i]<-paste0(test_pub_med$Authors[i], " ", "(", test_pub_med$Publication.Year[i], ")", " ", test_pub_med$Title[i], " ", test_pub_med$Journal.Book[i], " ", "PMID:", test_pub_med$PMID[i])
  }

PubMed <- data.frame(PubMed)

#print.table(test)
data.frame(PubMed) %>% 
 knitr:: kable("pipe") 

```

